Individual Partisan Harm and Utility in Redistricting

### 2021-11-05 paper/paper.Rmd
response slides with sections + add note to paper

We offer a reminder that geographic context is key to understanding common problems in political science; elections themselves are geographically determined.
Recent research offers important resolution of the degree of partisan sorting in the US [@enos:brown:21].
By combining those understandings with the necessities of redistricting, we are able to expand the localized aspect of harm.
Further, we suggest that while the efficiency gap may not incorporate geographic information, it often helps capture individual harm better than other common measures.
This is a great benefit as an indicator to detect extreme gerrymanders in cases where sufficiently local geographic data to simulate plans is not available.
We further clarify that common existing measures of partisan fairness -- while they may capture the difficulties offered to a party -- do not necessarily capture the representational harms incurred by individuals who live in districts which do not at all represent their preferences.

>>>>

We offer a reminder that geographic context is key to understanding common problems in political science; elections themselves are geographically determined.
<!-- people super hate this sentence above, which is fair, though is a problem in this lit -->
Recent research offers important resolution of the degree of partisan sorting in the US [@enos:brown:21].
By combining those understandings with the necessities of redistricting, we are able to expand the localized aspect of harm.
Further, we suggest that while the efficiency gap may not incorporate geographic information, it often helps capture individual harm better than other common measures.
This is a great benefit as an indicator to detect extreme gerrymanders in cases where sufficiently local geographic data to simulate plans is not available.
We further clarify that common existing measures of partisan fairness -- while they may capture the difficulties offered to a party -- do not necessarily capture the representational harms incurred by individuals who live in districts which do not at all represent their preferences.
